\thetitle

### 2020-07-27 writing/challenges.tex
simple touch ups to prose on challenges and mutate

A derivative challenge is the problem of simulating the programmer's
mistakes or, more precisely, the origin of impedance mismatches. Before a
programmer can try to find mistakes, mistakes have to be made.
Specifically, a necessary step to test the rational programmer is to find
a collection of  type mistakes in  mix-typed programs that is highly
representantive of both mistakes and programs ``in the wild.''
Unfortunately no such collection exists.  There is a good reason for that;
the kind of mistakes the rational programmer targets are easily detected
by unit tests and, even if they are tough to weed out, they do not make it
to code repositories.  In other words, the problem is how to generate a
sufficiently large and representantive corpus of type mistakes for a meaningful
experiment.  Following~\citet{lksfd-popl-2020} again, the solution is to
use mutation analysis~\cite{lipton1971fault, demillo1978hints,
jia2011analysis} to create mistakes in a synthetic manner. This process
yields a large number of buggy programs whose mixed-typed versions are
suitable subjects for our experiment.  The mutation analysis of Lazarek et
al, is, however, completely useless for creating impedance mismatches.

>>>>

A derivative challenge is the problem of simulating the programmer's
mistakes or, more precisely, the origin of impedance mismatches. Before a
programmer can try to find mistakes, mistakes have to be made.
Specifically, a necessary step to test the rational programmer is to find
a collection of  type mistakes in  mix-typed programs that is highly
representantive of both mistakes and programs ``in the wild.''
Unfortunately no such collection exists.  There is a good reason for that;
the kind of mistakes the rational programmer targets are easily detected
by unit tests and, even if their sources are hard to find, these mistakes do not make it
into code repositories with appropriate commit messages.  In other words, the problem is how to generate a
sufficiently large and representantive corpus of type mistakes for a meaningful
experiment.  Following~\citet{lksfd-popl-2020} again, the solution is to
use mutation analysis~\cite{lipton1971fault, demillo1978hints,
jia2011analysis} to create mistakes in a synthetic manner. This process
yields a large number of buggy programs whose mixed-typed versions are
suitable subjects for our experiment.  The mutation analysis of Lazarek et
al, is, however, completely useless for creating impedance mismatches.

### 2020-07-27 writing/mutate.tex
simple touch ups to prose on challenges and mutate

An important challenge from~\ref{sec:challenges} is the generation of
mix-typed programs with representative type mistakes. In this section, we
present our generation process and we argue that despite its synthetic
nature it results in a large corpus of programs with type mistakes that
are realistic and diverse.

>>>>

An important challenge from section~\ref{sec:challenges} is the generation of
mix-typed programs with representative impedance mismatches between
the typed components, their types, and the behavior of untyped components. In this section, we
present a generation process and argue that, despite its synthetic
nature, it yields a large corpus of programs with  realistic and diverse type mistakes.
